Low-Thrust Trajectory Design Near Asteroids Using Reachability Sets

### 2016-08-07 manuscript.tex
Adding detail to reachability section

\section{Introduction}

@@

\section{Asteroid Model}

@@

\subsection{Polyhedron Gravity Model}

@@

\subsection{Spacecraft Equations of Motion}

@@

\section{Reachability Set on \Poincare Section}

Define reachability set

Define \Poincare section following the method of Scheeres.
It is used in the periodic orbit determination~\cite{}

@@

\section{Numerical Simulation}

@@

\section{Conclusion}

>>>>

\section{Introduction}\label{sec:introduction}

@@

\section{Asteroid Model}\label{sec:asteroid_model}

@@

\subsection{Polyhedron Gravity Model}\label{sec:polyhedron_model}

@@

Mention that our model uses only 1024 faces for speed

Show the plot of the equilibrium position as a function of the number of faces and show that it's where the knee in the curve exists

\subsection{Spacecraft Equations of Motion}\label{sec:sc_eoms}

@@

\section{Reachability Set on \Poincare Section}\label{sec:reachability}

Typical optimal control methods, including both indirect and direct based methods, are highly dependent on an accurate initial guess.
For indirect optimization, which is based on the calclus of variations, this results in the well-known two-point boundary value problem.
Insight into the problem or insight by the designer is usually required to determine appropriate initial costates that will converge to the optimal solution and satisfy the desired constraints.
To avoid this issue, we utilize the concept of the reachiblity set on a lower dimensional \Poincare section.
By repeatedly constructing the reachability set we can achieve general transfers by determining set intersections on the \Poincare section.
This alleviates the need to determine an accurate initial guess while offering some insight into the dynamics of neighboring trajectories

The reachable set contains all possible trajectories that are achievable over a fixed time horizon from a defined initial condition, subject to the constraints of the system.
Reachability theory has been applied to collision avoidance and safety planning in aerospace systems~\cite{holzinger2009,holzinger2011b}.
The theory supporting reachabiilty analysis is directly derivable from optimal control theory~\cite{varaiya2000,lygeros2004}.
Analytic, computation of reachability sets is only possible for a small class of potential systems.
Here, we use numerical methods to solve an optimal control problem.
The solution of this optimal control problem approximates a single solution that lies on the reachable set.
\begin{figure}
    \centering
    \begin{scaletikzpicturetowidth}{0.5\textwidth}
    \begin{tikzpicture}[scale=\tikzscale]
        \coordinate [label=left:\textcolor{black}{\large \(\vec{x}_0\)}] (x0) at (-1,-2);
        \coordinate [label=below:\textcolor{black}{\large  \(\vec{x}_n\)}] (xn) at (1,1);
        \coordinate [label=left:\textcolor{black}{\large  \(\Sigma\)}] (sigma) at (-4,3);
        %\coordinate [label=below:\textcolor{black}{\large  \(P(\vec{x})\)}] (P) at (0,-3.5);
        % define the path of the flow with coordinates
        \coordinate [label=right:\textcolor{black}{}] (f1) at (5,-2);
        \coordinate [label=below:\textcolor{black}{\large  \(\phi(t,\vec{x}_0)\)}] (f2) at (2,-5);
        \coordinate [label=right:\textcolor{black}{}] (f3) at (-4,-4);
        \coordinate [label=right:\textcolor{black}{}] (f4) at (-4,-1);

    %   \draw[help lines] (-10,-10) grid (10,10); %grid
        \filldraw [black] (x0) circle [radius=3pt];
        \filldraw [black] (xn) circle [radius=3pt];

        \draw [ultra thick,black,->-](x0) to[out=20,in=90,distance=2cm] (f1) to[out=-90,in=0,distance=2cm] (f2) to[out=180,in=-45,distance=2cm] (f3) to[out=135,in=-135,distance=2cm] (f4) ;
        \draw [ultra thick, black,dashed,->] (f4) to[out=45,in=180,distance=1cm] ($(xn)-(2,0)$);

        \draw [ultra thick] plot [smooth cycle, tension=0.1, rotate=5] coordinates { (-4,-3) (4,-3) (4,3) (-4,3) };

        \draw [thick,dashed] (xn) circle [radius=2cm]; % reachability set

        \draw [thick,->] (xn) -- ($(xn) + (2.5,0)$);
        \draw [thick,rotate=45,->] (xn) -- ($(xn) + (2.5,0)$);
        \draw ($(xn) + (1,0)$) arc [start angle=0,end angle=45, radius=1];
        \node [draw=none] at (2.4,1.5) {\Large \(\theta_d\)};
        \draw [decorate,decoration={brace,amplitude=5pt},rotate=45] (xn) -- ($(xn) + (2,0)$);
        \node [draw=none] at ($ (xn) + (0,1) $) {\Large \( J \)};
    \end{tikzpicture}
    \end{scaletikzpicturetowidth}
    \caption{Reachability set on a \Poincare section\label{fig:reachability_set}}
\end{figure}

We seek to approximate the reachability set on a \Poincare section by solving an optimal control problem.
The \Poincare section is chosen in a manner similar to the previous work in both the three-body problem as well analysis performed around asteroids to determine periodic orbits.
Analysis in the three-body problem relies heaviliy on symmetries in the force fields.
However, in our system model the gravitational potential, given by~\cref{eq:potential}, has no symmetries.
In spite of this, it is still possible to determine periodic solutions through the application of a \Poincare map with surface of section chosen normal to surface in the phase space~\cite{scheeres2000}.
For a periodic orbit, the trajectories will intersect the \Poincare section at two distinct points every half orbit.
With the addition of a low thrust control input, we are able to expand the reachable set from a distinct point to a larger area on the \Poincare section.
\Cref{fig:reachability_set} illustrates this methodology.
Without any control input, the trajectories will intersect the \Poincare section at \( \vecbf{x}_n\).
The addition of a control input allows the spacecraft to depart from the natural dynamics and intersect the section at another location.
We use the cost function \( J \) to define a distance metric on the \Poincare section.
Maximization of \( J \), or the minimization of \( -J \), along various directions on the \Poincare section allows us to generate the larges reachability set under the bounded control input.

We define the \Poincare section as the surface normal to \( y = 0 \).
Following convention, the \Poincare map is defined as the map from one transversal crossing of the surface \( y = 0\) to the next.
Using the method of Reference~\cite{scheeres2000}, we are able to remove \( y \) and \( \dot{y} \), creating a four-dimensional map.
The \Poincare section, \( \Sigma \) then becomes
\begin{align}\label{eq:poincare_section}
    \Sigma = \braces{\parenth{x, \dot{x}, z, \dot{z}} | y(t_f) = 0 }.
\end{align}
We use this section to compute periodic orbits that serve as the initial and target of our transfer.
In addition, this section serves as a lower dimensional space upon which we approximate the reachability set.

An optimal control problem is defined by the cost function
\begin{align}\label{eq:cost}
    J = -\frac{1}{2} \left( \vecbf{x}(t_f) - \vecbf{x}_{n}(t_f)\right)^T 
    \begin{bmatrix}
        1 & 0 & 0 & 0 & 0 & 0 \\
        0 & 0 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & 0 & 0 \\
        0 & 0 & 0 & 0 & 0 & 1 \\
    \end{bmatrix}
    \left( \vecbf{x}(t_f) - \vecbf{x}_{n}(t_f)\right) ,
\end{align}
where \( \vecbf{x}_n(t_f) \) is the final state of a control-free trajectory, while the term \( \vecbf{x}(t_f)\) is the final state of a trajectory under the influence of the control input.
Maximization of the distance between \( \vecbf{x}_n \) and \(\vecbf{x} \), on the \Poincare section defined in~\cref{eq:poincare_section}, is equivalent to the minimization of \( J \) defined in~\cref{eq:cost}.
We ensure that the trajectories 
Define reachability set

Define \Poincare section following the method of Scheeres.
It is used in the periodic orbit determination.

@@

\section{Numerical Simulation}\label{sec:simulation}

@@

\section{Conclusions}\label{sec:conclusions}
